% Copyright (c) 2021-2023 Eclipse Arrowhead Project
%
% This program and the accompanying materials are made available under the
% terms of the Eclipse Public License 2.0 which is available at
% http://www.eclipse.org/legal/epl-2.0.
%
% SPDX-License-Identifier: EPL-2.0

\documentclass[a4paper]{arrowhead}

\usepackage[yyyymmdd]{datetime}
\usepackage{enumitem}
\usepackage{etoolbox}
\usepackage[utf8]{inputenc}
\usepackage{multirow}

\renewcommand{\dateseparator}{-}

\begin{document}

%% Arrowhead Document Properties
\ArrowheadTitle{Concepts Reference}
\ArrowheadType{Framework Description}
\ArrowheadTypeShort{FD}
\ArrowheadVersion{0.3}
\ArrowheadDate{\today}
\ArrowheadAuthor{Emanuel Palm and Jerker Delsing}
\ArrowheadOrganization{Eclipse Arrowhead}
\ArrowheadStatus{Proposal}
\ArrowheadContact{emanuel.palm@pinterop.se}
\ArrowheadAbstract{
  This document provides authoritative definitions for the most fundamental concepts of relevance to \textit{Eclipse Arrowhead}, a framework designed to facilitate the effective creation of service-oriented automation systems.
  It is meant to serve as foundation for other documents with relevance to the framework, providing a precise vocabulary untied to any specific practices or technologies.
  It does not contain any architectural patterns or definitions, which means that it, by itself, is not a sufficient foundation for designing Arrowhead systems.
  While its definitions are presented as a model, the document does not endorse any particular modeling language.
}
\ArrowheadFooter{\href{www.arrowhead.eu}{www.arrowhead.eu}}
\ArrowheadSetup
%%

%% Custom Document Commands
\newcommand{\GlossaryHyperRef}[2]{{\color{ArrowheadDarkBlue}\hyperref[sec:glossary:#1]{#2}}}
\newcommand{\GlossaryNameRef}[1]{{\color{ArrowheadDarkBlue}\nameref{sec:glossary:#1}}}
%%

%% Front Page
\ArrowheadFrontPage
%%

%% Table of Contents
\tableofcontents
\newpage
%%

\section{Introduction}
\label{sec:introduction}
\input{sections/introduction}

\section{Overview}
\label{sec:overview}
\input{sections/overview}

\section{Concepts}
\label{sec:concepts}
\input{sections/concepts}

\section{Conformance Requirements}
\label{sec:conformance}
\input{sections/conformance}

\section{Glossary}
\label{sec:glossary}
\input{sections/glossary}

\renewcommand{\bibsection}{\section{References}\label{sec:references}}
\bibliographystyle{arrowhead}
\bibliography{bibliography}

\newpage

\section{Revision History}
\label{sec:revision}

\subsection{Amendments}

\noindent\begin{tabularx}{\textwidth}{| p{1cm} | p{2cm} | p{1.25cm} | X | p{4cm} |} \hline
\rowcolor{gray!33} No. & Date & Version & Subject of Amendments & Author \\ \hline

1 & 2022-01-01 & 0.1 & Initial proposal. & Emanuel Palm \\ \hline
2 & 2022-02-11 & 0.2 & Made minor improvements to various figures and the Overview and Concepts sections. & Emanuel Palm \\ \hline
3 & 2023-02-17 & 0.3 & Revised and extended the Overview and Concepts sections in response to Sinetiq review. & Emanuel Palm \\ \hline

\end{tabularx}

\subsection{Quality Assurance}

\noindent\begin{tabularx}{\textwidth}{| p{1cm} | p{2cm} | p{1.25cm} | X |} \hline
\rowcolor{gray!33} No. & Date & Version & Approved by \\ \hline

1 & & & \\ \hline

\end{tabularx}

\end{document}