% Copyright (c) 2021 Eclipse Arrowhead Project
%
% This program and the accompanying materials are made available under the
% terms of the Eclipse Public License 2.0 which is available at
% http://www.eclipse.org/legal/epl-2.0.
%
% SPDX-License-Identifier: EPL-2.0

We expect the automation systems of today to keep becoming more and more computerized, digitized and interconnected.
By this we mean that more aspects of and surrounding automation machines will be handled by computers, more information will be made available to those computers and, finally, comparatively more such computers will be given the opportunity to collect, communicate and act on that information.
Manufacturing, transportation, energy distribution, medicine, recycling, as well as all other industrial sectors concerned with automation will be affected by this development.
It will lead to increased automation efficiency and flexibility, as machines become able to perform more of the work traditionally assigned to humans.
However, it will also lead to new magnitudes of complexity, not the least because of the renewed incentive to use more and more of these highly communicative machines.

The \GlossaryHyperRef{framework-arrowhead}{\textit{Arrowhead framework}} is designed to address this explosion of complexity.
It provides a foundation for \GlossaryHyperRef{communication-service-oriented}{\textit{service-oriented communication}} \cite{mackenzie2006reference} between automation systems and other computers, such that interoperability, security, safety, performance, and other major concerns can be addressed efficiently and effectively.
It notably allows for \GlossaryHyperRef{system}{system} \GlossaryHyperRef{capability}{capabilities} to be \GlossaryHyperRef{description}{described}, shared and exploited dynamically by communicating \GlossaryHyperRef{device}{devices}.

In this document, we, the Eclipse Arrowhead project, present an authoritative set of concept definitions, meant to serve as the fundamental language for describing Arrowhead-based system \GlossaryHyperRef{design}{designs}.
It exist to help mitigate compatibility and consistency issues in \GlossaryHyperRef{software}{software}, tooling, \GlossaryHyperRef{model}{models}, documentation and all other things of relevance to the Arrowhead framework.

\subsection{Primary Audiences}
\label{sec:introduction:audiences}

This document is being written and maintained for all who need precise and rigorous definitions of important Arrowhead concepts, which we understand to likely include the following groups:

\begin{itemize}
\item Advanced \GlossaryHyperRef{user}{users} of Arrowhead systems.
\item \GlossaryHyperRef{architect}{Architects} contributing to or extending the Arrowhead framework.
\item \GlossaryHyperRef{developer}{Developers} of Arrowhead systems, or of devices that are expected to host Arrowhead systems.
\item \GlossaryHyperRef{operator}{Operators} of Arrowhead systems.
\item \GlossaryHyperRef{researcher}{Researchers} concerned with analyzing or refining the Arrowhead framework or Arrowhead systems.
\end{itemize}

\subsection{Scope}
\label{sec:introduction:scope}

This document is intended to clearly define all technical concepts of fundamental importance to the Arrowhead framework.
It does not specify how Arrowhead-based automation systems ought to be designed.
This makes its purpose analogous to that of a dictionary.
Dictionaries define words.
They may give examples of how certain words may be used, but they do not require that those words be used for any particular purposes.
This document provides an Arrowhead vocabulary other documents or models may use to express software-centric automation system designs.

The concepts presented here are meant to be useful as a resource for advanced Arrowhead framework learners, as well as to serve as foundation for other documentation and modeling efforts.
This document does \textit{not} define an Arrowhead profile for SysML \cite{omg2019sysml}, or any other modeling language.
For those interested in using this document for software-architectural purposes, a description of how it can be used as a \GlossaryHyperRef{modelmeta}{metamodel} in the context of an ISO/IEC/IEEE 42010 \GlossaryHyperRef{kind-model}{model kind} is provided in Section \ref{sec:conformance:iso42010}.

\newpage

\subsection{Notational Conventions}
\label{sec:introduction:conventions}

The following conventions regarding diagrams depicting graphs, references and requirements are adhered to throughout this document.

\subsubsection{Graph Diagrams}

A box with a solid border and a name inside it denotes a named \GlossaryHyperRef{entity}{entity} and may represent any Arrowhead \GlossaryHyperRef{artifact}{artifact} or \GlossaryHyperRef{stakeholder}{stakeholder}.
A named arrow between boxes denotes the \GlossaryHyperRef{relationship}{relationship} implied by the name.
Relationship names are defined either here or in relation to the figures they are used in, unless their significance is considered obvious.
The following relationship names are defined here only:

\begin{enumerate}
\item \textit{conforms to}, which means that the origin entity satisfies all \GlossaryHyperRef{constraint}{constraints} implicitly and/or explicitly associated with the target entity;
\item \textit{extends}, which means that the origin entity \textit{conforms to} the target entity and inherits all of its \GlossaryHyperRef{attribute}{attributes} and relationships;
\item \textit{is}, which means that the origin entity \textit{extends} the target entity and is member of a group named after that target entity; and, finally,
\item \textit{has}, which means that the origin entity owns, or controls, the target entity.
\end{enumerate}

\paragraph{Quantifiers}
If a named arrow has an associated positive integer or range, which we refer to as a \textit{quantifier}, the relationship is to be considered as extending to the number of distinct entities indicated by that quantifier.
No quantifier being present implies a quantity of 1.
A range is denoted by $x..y$, where $x$ and $y$ are integers and $0 \leq x < y$.
If $y$ is substituted by $*$, the range must be understood to extend infinitely from $x$ (e.g. ``$1..*$'').

\paragraph{Groups}
A box with a dotted border represents a \textit{group}.
Groups have no other significance than to improve clarity, unless something else is indicated by text in its figure or the text adjacent to the figure.

\paragraph{Combined Arrows}
If two or more arrows are combined such that their source or target end is shared, a difference is made if a quantifier is closest to a shared or non-shared arrow part.
If it is closest to a shared part, the quantity must be understood to apply to the arrows of the combination collectively.
For example, if an arrow extends from one entity to three other entities and the quantifier is ``$0..1$'' at the shared part, the relationship extends to only zero or one of the three entities.
If a quantifier is closest to a non-shared part, the quantifier must be understood to only apply to the relationship of that arrow only.
Combined arrows may have quantifiers both at their shared and non-shared parts, which are associated with the quantifiers $0..*$ and $1$, respectively, if not explicitly specified.

\subsubsection{References}

Square brackets around numbers (e.g. \cite{delsing2017iot}) are references to the reference list in Section \ref{sec:references}.
The number within the brackets of any given reference corresponds to the entry with the same number in the reference list.

References within this document are hyperlinked, which means that those reading it electronically can click the references and immediately be taken to their targets.
Special treatment is given to references targeting Section \ref{sec:glossary}, the \nameref{sec:glossary}.
These are displayed as regular text rendered with blue color.

\subsubsection{Requirements}

Use of the terms \textbf{must}, \textbf{must not}, \textbf{should}, \textbf{should not} and \textbf{may} are to be interpreted as follows when used in this document: \textbf{must} and \textbf{must not} denote absolute requirements and prohibitions, respectively; \textbf{should} and \textbf{should not} denote recommendations that should be deviated from only if special circumstances make it relevant; and, finally, \textbf{may} denotes something being truly optional.

\subsection{Relationships to Other Documents}
\label{sec:introduction:relationships}

This document reuses or builds upon the concepts presented in the following works:

\begin{enumerate}

\item \textbf{IoT Automation: Arrowhead Framework} (IoTA:AF) \cite{delsing2017iot}, which significantly includes an overview of the \textit{local automation cloud} concept in its second chapter, as well as the \textit{Arrowhead framework architecture} in its third chapter.
The book most significantly represents the state of the Arrowhead framework up until it was written.
Even though the framework has evolved since then, it still represents the most comprehensive view of the framework.
While the strictly architectural aspects of IoTA:AF are outside the scope of this document, the two mentioned chapters contain several definition with a high degree of relevance.

\item \textbf{ISO/IEC/IEEE 42010 Systems and software engineering — Architecture description} (ISO42010) \cite{iso42010}, which outlines a standardized approach to structuring architectural documents and models.
The standard is adhered to in the sense that the definitions of this document are meant to be useful as a metamodel part of a so-called \GlossaryHyperRef{kind-model}{\textit{model kind}}, as defined by the standard.
No claim of conformance to the standard is made for this document on its own.
Please refer to Section \ref{sec:conformance:iso42010} for more details.

\item \textbf{Reference Model for Service Oriented Architecture} (SOA-RM) \cite{mackenzie2006reference}, which provides a standardized definition of Service-Oriented Architecture (SOA).
Communications between Arrowhead \GlossaryHyperRef{system}{systems} are expected to adhere to this paradigm.

\item \textbf{Reference Architecture Model Industrie 4.0} (RAMI4.0) \cite{adolphs2016reference}, which outlines an ontological and architectural view of \GlossaryHyperRef{industry40}{\textit{Industry 4.0}}.
The document may be seen as a predecessor to, or major influence on, the conceptual aspects of the Arrowhead framework.
In particular, the document describes how to model and design communicating industrial systems such that key Industry 4.0 characteristics can be facilitated, such as high degrees of dynamicity and interoperability.
However, as RAMI4.0 is a reference \textit{architecture} rather than a reference \textit{model}, we have only been concerned with what concepts it defines and what problems it frames.
This delimitation excludes its ``architectural layers'', ``life-cycle \& value-stream'' phases and ``hierarchical levels'', as well as the abstract design of its ``asset administrative shell''.
These excluded aspects are neither condemned nor endorsed by this document.
They are simply outside its scope.

\end{enumerate}

Only conformity with IoTA:AF and ISO42010 is observed strictly, which means that concept definitions presented here may diverge from those of the other two works.
All significant terminology differences are noted in the glossary of Section \ref{sec:glossary}, which briefly defines all concepts of relevance to this document.

\subsection{Section Overview}
\label{sec:introduction:sections}

The remaining sections of this document are organized as follows:
\vspace*{2mm}
\begin{itemize}[leftmargin=2cm,rightmargin=0pt,labelwidth=2cm,labelsep=0pt,itemindent=0pt,parsep=0.1cm,topsep=0.1cm,align=left]

\item[Section \ref{sec:introduction}]
This section.

\item[Section \ref{sec:overview}]
A brief and formal overview of Arrowhead, describing how its core concepts relate to each other.
The section also serves to provide a workable summary of the framework and to prepare readers for better understanding Section \ref{sec:concepts}.

\item[Section \ref{sec:concepts}]
A formal description of the most significant concepts of Arrowhead.
Each of its subsections is concerned with one primary concept, ranging from entities to systems-of-local-clouds.

\item[Section \ref{sec:conformance}]
A list of requirements, meant to help determine if a document or model referring to the concepts of this document can be considered conformant.
A special subsection on ISO/IEC/IEEE 42010 conformance is also provided.

\item[Section \ref{sec:glossary}]
Lists all significant terms and abbreviations presented in this document in alphabetical order.

\item[Section \ref{sec:references}]
Lists references to publications referred to in this document.

\item[Section \ref{sec:revision}]
Records the history of changes made to this document.

\end{itemize}
